Official Development Assistance and Institutional Quality on Undeveloped countries

### 2024-09-11 paper.Rmd
Oh sh!t here we go again

## Tablas informativas
```{r}
temp <- datos_paper %>% 
   filter(!year <  2002, !year > 2022, !country %in% c('SS')) %>%
   merge(my_countries) %>%
   merge(country_class) %>%
   group_by(`Income group`) %>%
   summarise('2002 - 2022' = sum(ODA.ALL))

@@

temp <- datos_paper %>% 
  mutate(y_range = case_when(year < 2007 ~ '2002 - 2006',
                             year < 2012 ~ '2007 - 2011',
                             year < 2017 ~ '2012 - 2016',
                             TRUE ~ '2017 - 2022')) %>%
  filter(!year <  2002, !year > 2022, !country %in% c('SS')) %>%
  merge(my_countries) %>%
  merge(country_class) %>%
  group_by(`Income group`, y_range) %>%
  summarise(sum=sum(ODA.ALL), .groups = "drop")

@@

temp <- datos_paper %>% 
  filter(!year <  2002, !year > 2022, !country %in% c('SS')) %>%
  merge(my_countries) %>%
  merge(country_class) %>%
  group_by(Region) %>%
  summarise('2002 - 2022' = sum(ODA.ALL))

@@

temp <- datos_paper %>% 
  mutate(y_range = case_when(year < 2007 ~ '2002 - 2006',
                             year < 2012 ~ '2007 - 2011',
                             year < 2017 ~ '2012 - 2016',
                             TRUE ~ '2017 - 2022')) %>%
  filter(!year <  2002, !year > 2022, !country %in% c('SS')) %>%
  merge(my_countries) %>%
  merge(country_class) %>%
  group_by(Region, y_range) %>%
  summarise(sum=sum(ODA.ALL), .groups = "drop")

@@

temp <- datos_paper %>% 
  filter(!year <  2002, !year > 2022, !country %in% c('SS', 'KP')) %>%
  merge(my_countries) %>%
  merge(country_class)

@@

# paises sin datos
delete_c <- c('SS', 'BT', 'ER', 'GW', 'KP', 'LB', 'NG', 'PS', 'SO', 'VU', 'FM', 'KI', 'SB', 'SY')
          #, 'KI',	'MR',	'SD',	'WS' Si se usa POL.CIV.LIB
          #, 'AF', 'CD', 'CI', 'DJ', 'KH', 'LR', 'MR', 'PG', 'ST', 'TJ', 'TL', 'UZ', 'VN', 'WS', 'ZW' Si se usa POV
          #, 'LK', 'PH' Si se usa ODA.ALL_LOG

@@

purtest(y, pmax = 4, exo = "intercept", test = "madwu")
```
### Cross-Sectional Dependance
```{r}
pcdtest(model_fe, test = c("lm"))
pcdtest(model_fe, test = c("cd"))
```
### Serial Correlation
```{r}
pbgtest(model_fe)
```
### Homoskedasticity
```{r}
bptest(hdi ~ ODA.PC*GOV_GOOD + GDP.PC + GOV, data = datos_model, studentize = F)
print('alternative hypothesis: Heteroscedasticidad')
```

@@

# Guardar Data
```{r}
save(f, delete_c, first_y, last_y, my_plot, model_ols, model_fe, model_re, file = "hdi_ODA.PCGOV_GOOD_GOV_GDP.PC.RData")
```

# Cargar Data
```{r}
#load("hdi_ODA.PCGOV_GOOD_GOV_GDP.PC_GROW.RData")
#load("hdi_ODA.PCGOV_GOOD_GOV_GDP.PC.RData")
#load("GDP.PC_ODA.PCGOV_GOOD_GOV_GROW.RData")
#load("POV_ODA.PCGOV_GOOD_GOV_GDP.PC_GROW.RData")
```

>>>>

## Tablas informativas
```{r}
temp <- datos_paper %>% 
   filter(!year <  2002, !year > 2022, !country %in% c('SS')) %>%
   merge(my_countries, by.x = "country", by.y = "iso2c") %>%
   merge(country_class) %>%
   group_by(`Income group`) %>%
   summarise('2002 - 2022' = sum(ODA.ALL))

@@

temp <- datos_paper %>% 
  mutate(y_range = case_when(year < 2007 ~ '2002 - 2006',
                             year < 2012 ~ '2007 - 2011',
                             year < 2017 ~ '2012 - 2016',
                             TRUE ~ '2017 - 2022')) %>%
  filter(!year <  2002, !year > 2022, !country %in% c('SS')) %>%
  merge(my_countries, by.x = "country", by.y = "iso2c") %>%
  merge(country_class) %>%
  group_by(`Income group`, y_range) %>%
  summarise(sum=sum(ODA.ALL), .groups = "drop")

@@

temp <- datos_paper %>% 
  filter(!year <  2002, !year > 2022, !country %in% c('SS')) %>%
  merge(my_countries, by.x = "country", by.y = "iso2c") %>%
  merge(country_class) %>%
  group_by(Region) %>%
  summarise('2002 - 2022' = sum(ODA.ALL))

@@

temp <- datos_paper %>% 
  mutate(y_range = case_when(year < 2007 ~ '2002 - 2006',
                             year < 2012 ~ '2007 - 2011',
                             year < 2017 ~ '2012 - 2016',
                             TRUE ~ '2017 - 2022')) %>%
  filter(!year <  2002, !year > 2022, !country %in% c('SS')) %>%
  merge(my_countries, by.x = "country", by.y = "iso2c") %>%
  merge(country_class) %>%
  group_by(Region, y_range) %>%
  summarise(sum=sum(ODA.ALL), .groups = "drop")

@@

temp <- datos_paper %>% 
  filter(!year <  2002, !year > 2022, !country %in% c('SS', 'KP')) %>%
  merge(my_countries, by.x = "country", by.y = "iso2c") %>%
  merge(country_class)

@@

# paises sin datos
delete_c <- c('SS', 'BT', 'ER', 'GW', 'KP', 'LB', 'NG', 'PS', 'SO', 'VU', 'FM', 'KI', 'SB', 'SY')
          #,	'MR',	'SD',	'WS' Si se usa POL.CIV.LIB
          #, 'AF', 'CD', 'CI', 'DJ', 'KH', 'LR', 'MR', 'PG', 'ST', 'TJ', 'TL', 'UZ', 'VN', 'WS', 'ZW' Si se usa POV
          #, 'LK', 'PH' Si se usa ODA.ALL_LOG

@@

purtest(y, pmax = 4, exo = "intercept", test = "madwu")
```
### Cross-Sectional Dependance
```{r}
pcdtest(model_fe, test = c("lm"))
pcdtest(model_fe, test = c("cd"))
```
### Serial Correlation
```{r}
pbgtest(model_fe)
```
### Homoskedasticity
```{r}
#bptest(hdi ~ ODA.PC*GOV_GOOD + GDP.PC + GOV, data = datos_model, studentize = F)
print('alternative hypothesis: Heteroscedasticidad')
```

@@

## Guardar Data
```{r}
#save(f, delete_c, first_y, last_y, my_plot, model_ols, model_fe, model_re, file = "hdi_ODA.PCGOV_GOOD_GOV_GDP.PC_POL.CIV.LIB.RData")
```

## Cargar Data
```{r}
#load("hdi_ODA.PCGOV_GOOD_GOV_GDP.PC_GROW.RData")
#load("hdi_ODA.PCGOV_GOOD_GOV_GDP.PC_POL.CIV.LIB.RData")
#load("hdi_ODA.PCGOV_GOOD_GOV_GDP.PC.RData")
#load("GDP.PC_ODA.PCGOV_GOOD_GOV_GROW.RData")
#load("POV_ODA.PCGOV_GOOD_GOV_GDP.PC_GROW.RData")
load("GOV_ODA.PC_hdi_GDP.PC.RData")
```

```{r}
write_xlsx(country_class %>% select(Code, Region, `Income group`) %>% filter(!is.na(Region), !is.na(`Income group`)) %>%
  merge(WDI_data$country, by.x='Code', by.y ='iso3c') %>% select(Code, iso2c, country, Region, `Income group`), 'group income.xls')
```
